### 2012-08-02 Doc/VRIPHYS2012/vriphys2012.tex
application on the birth simulation
git-svn-id: svn+ssh://scm.gforge.inria.fr/svnroot/sofa-shells@446 7b2761c9-2758-49ef-8c29-9c9f1e1aad1b

% TODO: maybe make a short table showing the convergence to the symmetric
% solution.

@@

% TODO:
% \CD{ - On this section,  we can maybe add some results from the CBM paper you did with Stephan especially  the figure 9 that illustrates the 3d contribution we list in the intro: i.e. Mapping of high resolution mesh on the curved surface of the shell.}
% Not enough space?

@@

To be able to predict results of complex surgical procedures a physically more
accurate approach is necessary. Using our shell finite element model we have
developed a prototype \cite{Kislinskiy2012} of new surgical simulation system
for preoperative planning. The element has been used to model deformations of
blood vessels and artificial patch. By performing a set of topological changes
we simulate the process of incising the vessel and suturing on a pre-specified
boundary. By iteratively adjusting the underlaying mesh we search for the
elastic equilibrium. Figure \ref{fig-chd} presents a screenshots of the
application prototype.

@@

@@

The second limitation is the choice of rigidly attached edge control
points. While it greatly simplifies the formulation the rigidity may cause
issues. In case of large compression of the element the results may be
unpredictable. This is however unlikely to occur because the element will
bend before reaching such configuration. It may, however, fail to maintain
even curvature of the surface if the element is subjected to large
stretching.

@@

\subsection{Conclusion} % {{{

@@

    % TODO: check this:
    % + Better conditioning (comparison between Comas model and ours in term of
    %   convergence of CG...)

@@

Because of the formulation of B\'ezier triangle that is intrinsically present
there is a clean and obvious way of mapping high-resolution mesh for
better visualisation. We also provide a mapping of forces and velocities
between simulation mesh and mechanical mesh for collision detection/response
and interaction with the mesh which are essential component for the surgical
simulator.

Finally examples showing the convergence to the optimal solution were also provided.

>>>>

@@

% TODO:
% \CD{ - On this section,  we can maybe add some results from the CBM paper you did with Stephan especially  the figure 9 that illustrates the 3d contribution we list in the intro: i.e. Mapping of high resolution mesh on the curved surface of the shell.}
% -- Not enough space?

@@

To be able to predict results of complex surgical procedures a physically more
accurate approach is necessary. Using our shell finite element model we have
developed a prototype \cite{Kislinskiy2012} of new surgical simulation system
for preoperative planning. The element has been used to model deformations of
blood vessels and artificial patches. By performing a set of topological changes
we simulate the process of incising the vessel and suturing on a pre-specified
boundary. By iteratively adjusting the underlaying mesh we search for the
elastic equilibrium. Figure \ref{fig-chd} presents a screenshots of the
application prototype.

@@

\subsection{Simulation of a Birth}

\FigureW{\linewidth}{birth}
{Screenshots from the simulation of child head during birth. Full visualisation (left) and the mechanical mesh (right).}

The purpose of another simulator kkk 
- Simulation of birth ! (Try to see where the tissue' stress is the highest)

The trajectory of the baby-head during the birth is predefined. The collisions response drives the deformations of the uterus.
Mechanically, the uterus is modeled with 127 shells solved by a direct solver (LDL factorization).
Up to 60 instantaneous contact spots, simulated at 6 FPS.
The goal is to reproduce the mechanical solicitations on the anatomical structure during the birth.

@@

The second limitation is the choice of rigidly attached control
points. While it greatly simplifies the formulation the rigidity may cause
issues. In case of large compression of the element the results may be
unpredictable. This is however unlikely to occur because the element will
bend before reaching such configuration. It may, however, fail to maintain
even curvature of the surface if the element is subjected to large
stretching.

@@

\section{Conclusion} % {{{

@@

@@

Because of the formulation of B\'ezier triangle that is intrinsically present
there is a clean and obvious way of mapping high-resolution mesh for better
visualisation. We also provide a technique of computing velocities of any point
on the surface and formula for back-projection of normal forces applied on the
surface onto the mechanical mesh. Those are form an essential component for the
surgical simulator as they are necessary if contact modeling between simulation
mesh and mechanical mesh is desired or other interaction with the mesh is
required.

At the end we present examples showing the convergence to the optimal solution
and the application of the model for several simulation tools.
